---
title: "Project 1"
output: html_notebook
---



```{r}
library("tidyverse")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
library("ggplot2")
library("ggrepel")
library("ggcorrplot")
library("DT")
library("dplyr")
```

```{r}
cases <- read_csv("COVID-19_cases_plus_census.csv")
```
```{r}
cases
```
```{r}
cases <- cases %>% mutate_if(is.character, factor)
dim(cases)
```
```{r}
cases_high <- cases %>% filter(confirmed_cases > 300000)
dim(cases_high)
```
```{r}
summary(cases_high[,1:10])
```
```{r}
ggplot(cases_high, mapping = aes(confirmed_cases)) + geom_histogram(bins = 10)
```
```{r}
library(sampling)
sampled_cases <- strata(cases, stratanames = "state", size = c(5), method = "srswor")
sampled_cases
```

```{r}
ggplot(data = cases) + 
  geom_point(mapping = aes(x = confirmed_cases, y = deaths)) + 
  facet_wrap(~ state, nrow = 6)
```


